---
title: "making rbarD plots using poppr"
author: "Guy Robinson"
date: "5/26/2021"
output: html_document
---

####################################################################################################
############### This is all of the code run for calculating the index of association. ##############
############### In the pipeline HTML, we have added a clear figure to display the Poppr ############
############### usage. Apologies for the mess. It was difficult to run each subsample ##############
############### independently. #####################################################################
####################################################################################################

#loading libraries
```{r, eval=F}
library(tidyverse)
library(RColorBrewer)
library(ggplot2)
library(vcfR)
library(adegenet)
library(poppr)
library(magrittr)

std <- function(x) sd(x)/sqrt(length(x))
```


#importing vcf file and converting into genind object
#https://cran.r-project.org/web/packages/vcfR/vignettes/converting_data.html
```{r, eval=F}
file_prep <- function(file) {
  isolate_vcf <- read.vcfR(file = file, verbose = FALSE) #import vcf file (can also be vcf.gz)
  isolate_genind <- vcfR2genind(isolate_vcf) #converts vcf into genind format
  isolate_genind$other$lineage <- c("SING", "SING", "SING", "SING", "SING", "T", "SING", "T", "O", "SING", "Q", "Q", "O", "J", "N", "SING", "N", "M", "M", "N", "SING", "P", "SING", "K", "N", "T", "Q", "SING", "P", "T", "N", "N", "P", "J", "J", "SING", "SING", "S", "S", "SING", "O", "SING", "SING", "T", "P", "T", "P", "R", "SING", "SING", "SING", "O", "R", "SING", "SING", "U", "SING", "SING", "E", "SING", "SING", "Q", "SING", "R", "O", "Q", "R", "SING", "SING", "R", "R", "R", "SING", "Q", "SING", "SING", "R", "O", "I", "M", "R", "E", "H", "SING", "G", "H", "F", "SING", "H", "SING", "L", "L", "O", "H", "H", "P", "R", "SING", "O", "T", "K", "E", "O", "SING", "O", "SING", "F", "G", "G", "M", "O", "Q", "P", "E", "T", "K", "R", "R", "SING", "O", "I", "U", "E", "SING", "P", "P", "R", "SING", "N", "R", "O", "O", "SING") #assigns predetermined lineages
  pop(isolate_genind) <- isolate_genind$other$lineage #assigns lineages as populations
  isolate_genclone <- as.genclone(isolate_genind) #creates genclone file for poppr analysis
}

ss1 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss2 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss3 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss4 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss5 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss6 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss7 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss8 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss9 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")
ss10 <- file_prep("ethiopia_fo_structure.0_05.vcf.gz_sub1.vcf.gz_rand.vcf.gz.tail.vcf")

#ss1 <- file_prep("/media/guy/Guy HardDrive/vcf_individuals_largerCollection/final_ld/data/ld/ld/eth_clonecorrected.vcf.vcf_nomiss.vcf.recode.vcf")

#done
```

#non-clone corrected Ia and Rbar calculations
```{r, eval=F}

#test_ia <- ia(isolate_genclone, sample = 10, valuereturn = TRUE)
#test_ia_clone <- ia(isolate_clone_correct, sample = 10, valuereturn = TRUE)
set.seed(100)
resmpl_ia_ss1 <- resample.ia(ss1, reps = 999, n=132)
resmpl_ia_ss2 <- resample.ia(ss2, reps = 999, n=132)
resmpl_ia_ss3 <- resample.ia(ss3, reps = 999, n=132)
resmpl_ia_ss4 <- resample.ia(ss4, reps = 999, n=132)
resmpl_ia_ss5 <- resample.ia(ss5, reps = 999, n=132)
resmpl_ia_ss6 <- resample.ia(ss6, reps = 999, n=132)
resmpl_ia_ss7 <- resample.ia(ss7, reps = 999, n=132)
resmpl_ia_ss8 <- resample.ia(ss8, reps = 999, n=132)
resmpl_ia_ss9 <- resample.ia(ss9, reps = 999, n=132)
resmpl_ia_ss10 <- resample.ia(ss10, reps = 999, n=132)
resmpl_ia_all <- rbind(resmpl_ia_ss1,
    resmpl_ia_ss2,
    resmpl_ia_ss3,
    resmpl_ia_ss4,
    resmpl_ia_ss5,
    resmpl_ia_ss6,
    resmpl_ia_ss7,
    resmpl_ia_ss8,
    resmpl_ia_ss9,
    resmpl_ia_ss10)

  write_delim(resmpl_ia_all, file = "results/all_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_all <- read_delim("results/all_isolates_ia_vals.txt", delim = "\t")
std(resmpl_ia_all$rbarD)


t <- ggplot(resmpl_ia_all, aes(x = rbarD)) +
  geom_histogram(bins=100) +
  geom_vline(xintercept = ia(ss1)[2]) +
#  geom_vline(xintercept = 0.0702, linetype=2) +
  geom_vline(xintercept = ia(clonecorrect(ss1))[2], linetype = 2) +
  xlab(expression(bar(r)[d]))
t

```


#separating populations before index of association calculation
```{r, eval=F}
obj1 <- seppop(ss1) #separates the genclone objects into a list of different populations
obj2 <- seppop(ss2)
obj3 <- seppop(ss3)
obj4 <- seppop(ss4)
obj5 <- seppop(ss5)
obj6 <- seppop(ss6)
obj7 <- seppop(ss7)
obj8 <- seppop(ss8)
obj9 <- seppop(ss9)
obj10 <- seppop(ss10)

####SS1
sing_genclone1 <- obj1$SING
e_genclone1 <- obj1$E
f_genclone1 <- obj1$F
g_genclone1 <- obj1$G
h_genclone1 <- obj1$H
i_genclone1 <- obj1$I
k_genclone1 <- obj1$K
l_genclone1 <- obj1$L
m_genclone1 <- obj1$M
n_genclone1 <- obj1$N
o_genclone1 <- obj1$O
p_genclone1 <- obj1$P
q_genclone1 <- obj1$Q
r_genclone1 <- obj1$R
s_genclone1 <- obj1$S
t_genclone1 <- obj1$T

####SS2
sing_genclone2 <- obj2$SING
e_genclone2 <- obj2$E
f_genclone2 <- obj2$F
g_genclone2 <- obj2$G
h_genclone2 <- obj2$H
i_genclone2 <- obj2$I
k_genclone2 <- obj2$K
l_genclone2 <- obj2$L
m_genclone2 <- obj2$M
n_genclone2 <- obj2$N
o_genclone2 <- obj2$O
p_genclone2 <- obj2$P
q_genclone2 <- obj2$Q
r_genclone2 <- obj2$R
s_genclone2 <- obj2$S
t_genclone2 <- obj2$T

####SS3
sing_genclone3 <- obj3$SING
e_genclone3 <- obj3$E
f_genclone3 <- obj3$F
g_genclone3 <- obj3$G
h_genclone3 <- obj3$H
i_genclone3 <- obj3$I
k_genclone3 <- obj3$K
l_genclone3 <- obj3$L
m_genclone3 <- obj3$M
n_genclone3 <- obj3$N
o_genclone3 <- obj3$O
p_genclone3 <- obj3$P
q_genclone3 <- obj3$Q
r_genclone3 <- obj3$R
s_genclone3 <- obj3$S
t_genclone3 <- obj3$T

####SS4
sing_genclone4 <- obj4$SING
e_genclone4 <- obj4$E
f_genclone4 <- obj4$F
g_genclone4 <- obj4$G
h_genclone4 <- obj4$H
i_genclone4 <- obj4$I
k_genclone4 <- obj4$K
l_genclone4 <- obj4$L
m_genclone4 <- obj4$M
n_genclone4 <- obj4$N
o_genclone4 <- obj4$O
p_genclone4 <- obj4$P
q_genclone4 <- obj4$Q
r_genclone4 <- obj4$R
s_genclone4 <- obj4$S
t_genclone4 <- obj4$T

####SS5
sing_genclone5 <- obj5$SING
e_genclone5 <- obj5$E
f_genclone5 <- obj5$F
g_genclone5 <- obj5$G
h_genclone5 <- obj5$H
i_genclone5 <- obj5$I
k_genclone5 <- obj5$K
l_genclone5 <- obj5$L
m_genclone5 <- obj5$M
n_genclone5 <- obj5$N
o_genclone5 <- obj5$O
p_genclone5 <- obj5$P
q_genclone5 <- obj5$Q
r_genclone5 <- obj5$R
s_genclone5 <- obj5$S
t_genclone5 <- obj5$T

####SS6
sing_genclone6 <- obj6$SING
e_genclone6 <- obj6$E
f_genclone6 <- obj6$F
g_genclone6 <- obj6$G
h_genclone6 <- obj6$H
i_genclone6 <- obj6$I
k_genclone6 <- obj6$K
l_genclone6 <- obj6$L
m_genclone6 <- obj6$M
n_genclone6 <- obj6$N
o_genclone6 <- obj6$O
p_genclone6 <- obj6$P
q_genclone6 <- obj6$Q
r_genclone6 <- obj6$R
s_genclone6 <- obj6$S
t_genclone6 <- obj6$T

####SS7
sing_genclone7 <- obj7$SING
e_genclone7 <- obj7$E
f_genclone7 <- obj7$F
g_genclone7 <- obj7$G
h_genclone7 <- obj7$H
i_genclone7 <- obj7$I
k_genclone7 <- obj7$K
l_genclone7 <- obj7$L
m_genclone7 <- obj7$M
n_genclone7 <- obj7$N
o_genclone7 <- obj7$O
p_genclone7 <- obj7$P
q_genclone7 <- obj7$Q
r_genclone7 <- obj7$R
s_genclone7 <- obj7$S
t_genclone7 <- obj7$T

####SS8
sing_genclone8 <- obj8$SING
e_genclone8 <- obj8$E
f_genclone8 <- obj8$F
g_genclone8 <- obj8$G
h_genclone8 <- obj8$H
i_genclone8 <- obj8$I
k_genclone8 <- obj8$K
l_genclone8 <- obj8$L
m_genclone8 <- obj8$M
n_genclone8 <- obj8$N
o_genclone8 <- obj8$O
p_genclone8 <- obj8$P
q_genclone8 <- obj8$Q
r_genclone8 <- obj8$R
s_genclone8 <- obj8$S
t_genclone8 <- obj8$T


####SS9
sing_genclone9 <- obj9$SING
e_genclone9 <- obj9$E
f_genclone9 <- obj9$F
g_genclone9 <- obj9$G
h_genclone9 <- obj9$H
i_genclone9 <- obj9$I
k_genclone9 <- obj9$K
l_genclone9 <- obj9$L
m_genclone9 <- obj9$M
n_genclone9 <- obj9$N
o_genclone9 <- obj9$O
p_genclone9 <- obj9$P
q_genclone9 <- obj9$Q
r_genclone9 <- obj9$R
s_genclone9 <- obj9$S
t_genclone9 <- obj9$T

####SS10
sing_genclone10 <- obj1$SING
e_genclone10 <- obj10$E
f_genclone10 <- obj10$F
g_genclone10 <- obj10$G
h_genclone10 <- obj10$H
i_genclone10 <- obj10$I
j_genclone10 <- obj10$J
k_genclone10 <- obj10$K
l_genclone10 <- obj10$L
m_genclone10 <- obj10$M
n_genclone10 <- obj10$N
o_genclone10 <- obj10$O
p_genclone10 <- obj10$P
q_genclone10 <- obj10$Q
r_genclone10 <- obj10$R
s_genclone10 <- obj10$S
t_genclone10 <- obj10$T
U_genclone10 <- obj10$U
  
```

#calculations of rbar and Ia -- Sing
```{r, eval=F}
resmpl_ia_ss1_sing <- resample.ia(sing_genclone1, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss2_sing <- resample.ia(sing_genclone2, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss3_sing <- resample.ia(sing_genclone3, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss4_sing <- resample.ia(sing_genclone4, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss5_sing <- resample.ia(sing_genclone5, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss6_sing <- resample.ia(sing_genclone6, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss7_sing <- resample.ia(sing_genclone7, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss8_sing <- resample.ia(sing_genclone8, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss9_sing <- resample.ia(sing_genclone9, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_ss10_sing <- resample.ia(sing_genclone10, reps = 999, n=(nrow(as.data.frame(sing_genclone1))-1))
resmpl_ia_sing <- rbind(resmpl_ia_ss1_sing,
    resmpl_ia_ss2_sing,
    resmpl_ia_ss3_sing,
    resmpl_ia_ss4_sing,
    resmpl_ia_ss5_sing,
    resmpl_ia_ss6_sing,
    resmpl_ia_ss7_sing,
    resmpl_ia_ss8_sing,
    resmpl_ia_ss9_sing,
    resmpl_ia_ss10_sing)
```

#calculations of rbar and Ia -- e
```{r, eval=F}
resmpl_ia_ss1_e <- resample.ia(e_genclone1, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss2_e <- resample.ia(e_genclone2, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss3_e <- resample.ia(e_genclone3, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss4_e <- resample.ia(e_genclone4, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss5_e <- resample.ia(e_genclone5, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss6_e <- resample.ia(e_genclone6, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss7_e <- resample.ia(e_genclone7, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss8_e <- resample.ia(e_genclone8, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss9_e <- resample.ia(e_genclone9, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_ss10_e <- resample.ia(e_genclone10, reps = 999, n=(nrow(as.data.frame(e_genclone1))-1))
resmpl_ia_e <- rbind(resmpl_ia_ss1_e,
    resmpl_ia_ss2_e,
    resmpl_ia_ss3_e,
    resmpl_ia_ss4_e,
    resmpl_ia_ss5_e,
    resmpl_ia_ss6_e,
    resmpl_ia_ss7_e,
    resmpl_ia_ss8_e,
    resmpl_ia_ss9_e,
    resmpl_ia_ss10_e)
```

#calculations of rbar and Ia -- f
```{r, eval=F}
resmpl_ia_ss1_f <- resample.ia(f_genclone1, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss2_f <- resample.ia(f_genclone2, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss3_f <- resample.ia(f_genclone3, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss4_f <- resample.ia(f_genclone4, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss5_f <- resample.ia(f_genclone5, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss6_f <- resample.ia(f_genclone6, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss7_f <- resample.ia(f_genclone7, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss8_f <- resample.ia(f_genclone8, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss9_f <- resample.ia(f_genclone9, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_ss10_f <- resample.ia(f_genclone10, reps = 999, n=(nrow(as.data.frame(f_genclone1))-1))
resmpl_ia_f <- rbind(resmpl_ia_ss1_f,
    resmpl_ia_ss2_f,
    resmpl_ia_ss3_f,
    resmpl_ia_ss4_f,
    resmpl_ia_ss5_f,
    resmpl_ia_ss6_f,
    resmpl_ia_ss7_f,
    resmpl_ia_ss8_f,
    resmpl_ia_ss9_f,
    resmpl_ia_ss10_f)
```

#calculations of rbar and Ia -- g #####Ignored due to too few isolates
```{r, eval=F}
#resmpl_ia_ss1_g <- resample.ia(g_genclone1, reps = 999, n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss2_g <- resample.ia(g_genclone2, reps = 999, n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss3_g <- resample.ia(g_genclone3, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss4_g <- resample.ia(g_genclone4, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss5_g <- resample.ia(g_genclone5, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss6_g <- resample.ia(g_genclone6, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss7_g <- resample.ia(g_genclone7, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss8_g <- resample.ia(g_genclone8, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss9_g <- resample.ia(g_genclone9, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_ss10_g <- resample.ia(g_genclone10, reps = 999, #n=(nrow(as.data.frame(g_genclone1))-1))
#resmpl_ia_g <- rbind(resmpl_ia_ss1_g,
#    resmpl_ia_ss2_g,
#    resmpl_ia_ss3_g,
#    resmpl_ia_ss4_g,
#    resmpl_ia_ss5_g,
#    resmpl_ia_ss6_g,
#    resmpl_ia_ss7_g,
#    resmpl_ia_ss8_g,
#    resmpl_ia_ss9_g,
#    resmpl_ia_ss10_g)
```

#calculations of rbar and Ia -- h
```{r, eval=F}
resmpl_ia_ss1_h <- resample.ia(h_genclone1, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss2_h <- resample.ia(h_genclone2, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss3_h <- resample.ia(h_genclone3, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss4_h <- resample.ia(h_genclone4, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss5_h <- resample.ia(h_genclone5, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss6_h <- resample.ia(h_genclone6, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss7_h <- resample.ia(h_genclone7, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss8_h <- resample.ia(h_genclone8, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss9_h <- resample.ia(h_genclone9, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_ss10_h <- resample.ia(h_genclone10, reps = 999, n=(nrow(as.data.frame(h_genclone1))-1))
resmpl_ia_h <- rbind(resmpl_ia_ss1_h,
    resmpl_ia_ss2_h,
    resmpl_ia_ss3_h,
    resmpl_ia_ss4_h,
    resmpl_ia_ss5_h,
    resmpl_ia_ss6_h,
    resmpl_ia_ss7_h,
    resmpl_ia_ss8_h,
    resmpl_ia_ss9_h,
    resmpl_ia_ss10_h)
```

#calculations of rbar and Ia -- i
```{r, eval=F}
resmpl_ia_ss1_i <- resample.ia(i_genclone1, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss2_i <- resample.ia(i_genclone2, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss3_i <- resample.ia(i_genclone3, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss4_i <- resample.ia(i_genclone4, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss5_i <- resample.ia(i_genclone5, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss6_i <- resample.ia(i_genclone6, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss7_i <- resample.ia(i_genclone7, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss8_i <- resample.ia(i_genclone8, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss9_i <- resample.ia(i_genclone9, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_ss10_i <- resample.ia(i_genclone10, reps = 999, n=(nrow(as.data.frame(i_genclone1))-1))
resmpl_ia_i <- rbind(resmpl_ia_ss1_i,
    resmpl_ia_ss2_i,
    resmpl_ia_ss3_i,
    resmpl_ia_ss4_i,
    resmpl_ia_ss5_i,
    resmpl_ia_ss6_i,
    resmpl_ia_ss7_i,
    resmpl_ia_ss8_i,
    resmpl_ia_ss9_i,
    resmpl_ia_ss10_i)
```

#calculations of rbar and Ia -- k
```{r, eval=F}
resmpl_ia_ss1_k <- resample.ia(k_genclone1, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss2_k <- resample.ia(k_genclone2, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss3_k <- resample.ia(k_genclone3, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss4_k <- resample.ia(k_genclone4, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss5_k <- resample.ia(k_genclone5, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss6_k <- resample.ia(k_genclone6, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss7_k <- resample.ia(k_genclone7, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss8_k <- resample.ia(k_genclone8, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss9_k <- resample.ia(k_genclone9, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_ss10_k <- resample.ia(k_genclone10, reps = 999, n=(nrow(as.data.frame(k_genclone1))-1))
resmpl_ia_k <- rbind(resmpl_ia_ss1_k,
    resmpl_ia_ss2_k,
    resmpl_ia_ss3_k,
    resmpl_ia_ss4_k,
    resmpl_ia_ss5_k,
    resmpl_ia_ss6_k,
    resmpl_ia_ss7_k,
    resmpl_ia_ss8_k,
    resmpl_ia_ss9_k,
    resmpl_ia_ss10_k)
```

#calculations of rbar and Ia -- l
```{r, eval=F}
resmpl_ia_ss1_l <- resample.ia(l_genclone1, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss2_l <- resample.ia(l_genclone2, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss3_l <- resample.ia(l_genclone3, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss4_l <- resample.ia(l_genclone4, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss5_l <- resample.ia(l_genclone5, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss6_l <- resample.ia(l_genclone6, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss7_l <- resample.ia(l_genclone7, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss8_l <- resample.ia(l_genclone8, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss9_l <- resample.ia(l_genclone9, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_ss10_l <- resample.ia(l_genclone10, reps = 999, n=(nrow(as.data.frame(l_genclone1))-1))
resmpl_ia_l <- rbind(resmpl_ia_ss1_l,
    resmpl_ia_ss2_l,
    resmpl_ia_ss3_l,
    resmpl_ia_ss4_l,
    resmpl_ia_ss5_l,
    resmpl_ia_ss6_l,
    resmpl_ia_ss7_l,
    resmpl_ia_ss8_l,
    resmpl_ia_ss9_l,
    resmpl_ia_ss10_l)
```

#calculations of rbar and Ia -- m
```{r, eval=F}
resmpl_ia_ss1_m <- resample.ia(m_genclone1, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss2_m <- resample.ia(m_genclone2, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss3_m <- resample.ia(m_genclone3, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss4_m <- resample.ia(m_genclone4, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss5_m <- resample.ia(m_genclone5, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss6_m <- resample.ia(m_genclone6, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss7_m <- resample.ia(m_genclone7, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss8_m <- resample.ia(m_genclone8, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss9_m <- resample.ia(m_genclone9, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_ss10_m <- resample.ia(m_genclone10, reps = 999, n=(nrow(as.data.frame(m_genclone1))-1))
resmpl_ia_m <- rbind(resmpl_ia_ss1_m,
    resmpl_ia_ss2_m,
    resmpl_ia_ss3_m,
    resmpl_ia_ss4_m,
    resmpl_ia_ss5_m,
    resmpl_ia_ss6_m,
    resmpl_ia_ss7_m,
    resmpl_ia_ss8_m,
    resmpl_ia_ss9_m,
    resmpl_ia_ss10_m)
```

#calculations of rbar and Ia -- n
```{r, eval=F}
resmpl_ia_ss1_n <- resample.ia(n_genclone1, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss2_n <- resample.ia(n_genclone2, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss3_n <- resample.ia(n_genclone3, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss4_n <- resample.ia(n_genclone4, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss5_n <- resample.ia(n_genclone5, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss6_n <- resample.ia(n_genclone6, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss7_n <- resample.ia(n_genclone7, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss8_n <- resample.ia(n_genclone8, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss9_n <- resample.ia(n_genclone9, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_ss10_n <- resample.ia(n_genclone10, reps = 999, n=(nrow(as.data.frame(n_genclone1))-1))
resmpl_ia_n <- rbind(resmpl_ia_ss1_n,
    resmpl_ia_ss2_n,
    resmpl_ia_ss3_n,
    resmpl_ia_ss4_n,
    resmpl_ia_ss5_n,
    resmpl_ia_ss6_n,
    resmpl_ia_ss7_n,
    resmpl_ia_ss8_n,
    resmpl_ia_ss9_n,
    resmpl_ia_ss10_n)
```

#calculations of rbar and Ia -- o
```{r, eval=F}
resmpl_ia_ss1_o <- resample.ia(o_genclone1, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss2_o <- resample.ia(o_genclone2, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss3_o <- resample.ia(o_genclone3, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss4_o <- resample.ia(o_genclone4, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss5_o <- resample.ia(o_genclone5, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss6_o <- resample.ia(o_genclone6, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss7_o <- resample.ia(o_genclone7, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss8_o <- resample.ia(o_genclone8, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss9_o <- resample.ia(o_genclone9, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_ss10_o <- resample.ia(o_genclone10, reps = 999, n=(nrow(as.data.frame(o_genclone1))-1))
resmpl_ia_o <- rbind(resmpl_ia_ss1_o,
    resmpl_ia_ss2_o,
    resmpl_ia_ss3_o,
    resmpl_ia_ss4_o,
    resmpl_ia_ss5_o,
    resmpl_ia_ss6_o,
    resmpl_ia_ss7_o,
    resmpl_ia_ss8_o,
    resmpl_ia_ss9_o,
    resmpl_ia_ss10_o)
```

#calculations of rbar and Ia -- p
```{r, eval=F}
resmpl_ia_ss1_p <- resample.ia(p_genclone1, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss2_p <- resample.ia(p_genclone2, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss3_p <- resample.ia(p_genclone3, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss4_p <- resample.ia(p_genclone4, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss5_p <- resample.ia(p_genclone5, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss6_p <- resample.ia(p_genclone6, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss7_p <- resample.ia(p_genclone7, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss8_p <- resample.ia(p_genclone8, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss9_p <- resample.ia(p_genclone9, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_ss10_p <- resample.ia(p_genclone10, reps = 999, n=(nrow(as.data.frame(p_genclone1))-1))
resmpl_ia_p <- rbind(resmpl_ia_ss1_p,
    resmpl_ia_ss2_p,
    resmpl_ia_ss3_p,
    resmpl_ia_ss4_p,
    resmpl_ia_ss5_p,
    resmpl_ia_ss6_p,
    resmpl_ia_ss7_p,
    resmpl_ia_ss8_p,
    resmpl_ia_ss9_p,
    resmpl_ia_ss10_p)
```

#calculations of rbar and Ia -- q
```{r, eval=F}
resmpl_ia_ss1_q <- resample.ia(q_genclone1, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss2_q <- resample.ia(q_genclone2, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss3_q <- resample.ia(q_genclone3, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss4_q <- resample.ia(q_genclone4, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss5_q <- resample.ia(q_genclone5, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss6_q <- resample.ia(q_genclone6, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss7_q <- resample.ia(q_genclone7, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss8_q <- resample.ia(q_genclone8, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss9_q <- resample.ia(q_genclone9, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_ss10_q <- resample.ia(q_genclone10, reps = 999, n=(nrow(as.data.frame(q_genclone1))-1))
resmpl_ia_q <- rbind(resmpl_ia_ss1_q,
    resmpl_ia_ss2_q,
    resmpl_ia_ss3_q,
    resmpl_ia_ss4_q,
    resmpl_ia_ss5_q,
    resmpl_ia_ss6_q,
    resmpl_ia_ss7_q,
    resmpl_ia_ss8_q,
    resmpl_ia_ss9_q,
    resmpl_ia_ss10_q)
```

#calculations of rbar and Ia -- r
```{r, eval=F}
resmpl_ia_ss1_r <- resample.ia(r_genclone1, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss2_r <- resample.ia(r_genclone2, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss3_r <- resample.ia(r_genclone3, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss4_r <- resample.ia(r_genclone4, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss5_r <- resample.ia(r_genclone5, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss6_r <- resample.ia(r_genclone6, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss7_r <- resample.ia(r_genclone7, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss8_r <- resample.ia(r_genclone8, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss9_r <- resample.ia(r_genclone9, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_ss10_r <- resample.ia(r_genclone10, reps = 999, n=(nrow(as.data.frame(r_genclone1))-1))
resmpl_ia_r <- rbind(resmpl_ia_ss1_r,
    resmpl_ia_ss2_r,
    resmpl_ia_ss3_r,
    resmpl_ia_ss4_r,
    resmpl_ia_ss5_r,
    resmpl_ia_ss6_r,
    resmpl_ia_ss7_r,
    resmpl_ia_ss8_r,
    resmpl_ia_ss9_r,
    resmpl_ia_ss10_r)
```

#calculations of rbar and Ia -- s
```{r, eval=F}
resmpl_ia_ss1_s <- resample.ia(s_genclone1, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss2_s <- resample.ia(s_genclone2, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss3_s <- resample.ia(s_genclone3, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss4_s <- resample.ia(s_genclone4, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss5_s <- resample.ia(s_genclone5, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss6_s <- resample.ia(s_genclone6, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss7_s <- resample.ia(s_genclone7, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss8_s <- resample.ia(s_genclone8, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss9_s <- resample.ia(s_genclone9, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_ss10_s <- resample.ia(s_genclone10, reps = 999, n=(nrow(as.data.frame(s_genclone1))-1))
resmpl_ia_s <- rbind(resmpl_ia_ss1_s,
    resmpl_ia_ss2_s,
    resmpl_ia_ss3_s,
    resmpl_ia_ss4_s,
    resmpl_ia_ss5_s,
    resmpl_ia_ss6_s,
    resmpl_ia_ss7_s,
    resmpl_ia_ss8_s,
    resmpl_ia_ss9_s,
    resmpl_ia_ss10_s)
```

#calculations of rbar and Ia -- t
```{r, eval=F}
resmpl_ia_ss1_t <- resample.ia(t_genclone1, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss2_t <- resample.ia(t_genclone2, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss3_t <- resample.ia(t_genclone3, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss4_t <- resample.ia(t_genclone4, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss5_t <- resample.ia(t_genclone5, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss6_t <- resample.ia(t_genclone6, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss7_t <- resample.ia(t_genclone7, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss8_t <- resample.ia(t_genclone8, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss9_t <- resample.ia(t_genclone9, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_ss10_t <- resample.ia(t_genclone10, reps = 999, n=(nrow(as.data.frame(t_genclone1))-1))
resmpl_ia_t <- rbind(resmpl_ia_ss1_t,
    resmpl_ia_ss2_t,
    resmpl_ia_ss3_t,
    resmpl_ia_ss4_t,
    resmpl_ia_ss5_t,
    resmpl_ia_ss6_t,
    resmpl_ia_ss7_t,
    resmpl_ia_ss8_t,
    resmpl_ia_ss9_t,
    resmpl_ia_ss10_t)
```


#writing out files for later analysis and figure making
```{r, eval=F}
write_delim(resmpl_ia_e, file = "results/E_isolates_ia_vals.txt", delim = "\t")
#write_delim(resmpl_ia_f, file = "results/F_isolates_ia_vals.txt", delim = "\t")
#write_delim(resmpl_ia_g, file = "results/G_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_h, file = "results/H_isolates_ia_vals.txt", delim = "\t")
#write_delim(resmpl_ia_i, file = "results/I_isolates_ia_vals.txt", delim = "\t")
#write_delim(resmpl_ia_k, file = "results/K_isolates_ia_vals.txt", delim = "\t")
#write_delim(resmpl_ia_l, file = "results/L_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_m, file = "results/M_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_n, file = "results/N_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_o, file = "results/O_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_p, file = "results/P_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_q, file = "results/Q_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_r, file = "results/R_isolates_ia_vals.txt", delim = "\t")
#write_delim(resmpl_ia_s, file = "results/S_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_t, file = "results/T_isolates_ia_vals.txt", delim = "\t")
write_delim(resmpl_ia_sing, file = "results/Singleton_isolates_ia_vals.txt", delim = "\t")

resmpl_ia_e <- read_delim(file = "results/E_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_h <- read_delim(file = "results/H_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_m <- read_delim(file = "results/M_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_n <- read_delim(file = "results/N_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_o <- read_delim(file = "results/O_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_p <- read_delim(file = "results/P_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_q <- read_delim(file = "results/Q_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_r <- read_delim(file = "results/R_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_t <- read_delim(file = "results/T_isolates_ia_vals.txt", delim = "\t")
resmpl_ia_sing <- read_delim(file = "results/Singleton_isolates_ia_vals.txt", delim = "\t")

std(resmpl_ia_e$rbarD)
std(resmpl_ia_h$rbarD)
std(resmpl_ia_m$rbarD)
std(resmpl_ia_n$rbarD)
std(resmpl_ia_o$rbarD)
std(resmpl_ia_p$rbarD)
std(resmpl_ia_q$rbarD)
std(resmpl_ia_r$rbarD)
std(resmpl_ia_t$rbarD)
std(resmpl_ia_sing$rbarD)



```

#plotting
```{r, eval=F}
resmpl_ia_e$name <- "E"
#resmpl_ia_f$name <- "F"
resmpl_ia_h$name <- "H"
#resmpl_ia_k$name <- "K"
resmpl_ia_m$name <- "M"
resmpl_ia_n$name <- "N"
resmpl_ia_o$name <- "O"
resmpl_ia_p$name <- "P"
resmpl_ia_q$name <- "Q"
resmpl_ia_r$name <- "R"
resmpl_ia_t$name <- "T"
resmpl_ia_sing$name <- "SING"

complete_ia <- rbind(
  resmpl_ia_e,
#resmpl_ia_f,
resmpl_ia_h,
#resmpl_ia_k,
resmpl_ia_m,
resmpl_ia_n,
resmpl_ia_o,
resmpl_ia_p,
resmpl_ia_q,
resmpl_ia_r,
resmpl_ia_t,
resmpl_ia_sing
)

t <- ggplot(complete_ia, aes(x=rbarD, y=Ia)) +
  geom_point(aes(color=name)) +
  scale_color_brewer(palette = "Paired")

#######################################

resmpl_ia_all$name <- "All"
test <- rbind(complete_ia, resmpl_ia_all)

t <- ggplot(complete_ia, aes(x=name, y=rbarD)) +
  geom_boxplot(aes(fill=name)) +
  scale_color_brewer(palette = "Paired") +
  theme_bw() +
  xlab("Lineage") +
  ylab(expression(Index~of~Association~(R[d])))

```

